Leveraging Sparsity to Speed Up Polynomial Feature Expansions of CSR Matrices Using $K$-Simplex Numbers

### 2018-03-08 paper/Final/sparse_poly_icml.tex
fixed tensor size

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Speeding Up Polynomial Feature Expansions of Sparse CSR Matrices Using $K$-Simplex Numbers}

@@

\twocolumn[

@@

\author{
  Nystrom, Andrew\\
  \texttt{nystrom@google.com}
  \and
  Hughes, John\\
  \texttt{jfh@cs.brown.edu}
}
\title{Speeding Up Polynomial Feature Expansions of Sparse CSR Matrices Using $K$-Simplex Numbers}
\maketitle

@@

\date{}

@@

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
%\footnotetext{hi}

@@

\subsection{Third Degree Interaction Mapping}
For $K=3$, we can no longer view the necessary function as mapping matrix coordinates to cell values, but rather, $2x2$ tensor coordinates to cell values.
For simplicity, we will instead list the column index tuples and their necessary mappings in a table.
We shall consider the case of $D=5$.

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Leveraging Sparsity to Speed Up Polynomial Feature Expansions of CSR Matrices Using $K$-Simplex Numbers}

@@

\twocolumn[
\icmltitle{Leveraging Sparsity to Speed Up Polynomial Feature Expansions of CSR Matrices Using $K$-Simplex Numbers}

@@

\begin{icmlauthorlist}
\icmlauthor{Andrew Nystrom}{google}
\icmlauthor{John Hughes}{brown}
\end{icmlauthorlist}

\icmlaffiliation{google}{Google Inc.}
\icmlaffiliation{brown}{Brown University}

\icmlcorrespondingauthor{Andrew Nystrom}{nystrom@google.com}
\icmlcorrespondingauthor{John Hughes}{jfh@cs.brown.edu}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{csr, polynomial, sparse, expansion, triangle, tetrahedral, simplex}

@@

@@

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
%\footnotetext{hi}

@@

\subsection{Third Degree Interaction Mapping}
For $K=3$, we can no longer view the necessary function as mapping matrix coordinates to cell values, but rather, $DxDxD$ tensor coordinates to cell values.
For simplicity, we will instead list the column index tuples and their necessary mappings in a table.
We shall consider the case of $D=5$.
